---
title: "Region and Time Conversion"
author: "L. Drouet"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Region and Time Conversion}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style type="text/css">
img, table, table th, table td {
  border: none;
}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(ggplot2)
```

## Region conversion

In this section, we convert a dataset containing the GDP of
all countries into a 17-region mapping of the WITCH model, then into the 
5-region mapping used in the SSP database.


First, let's create the initial database, we will extract the GDP in 2005
from the default_weights. The column names have to be renamed.
By convention, column names must be "iso3" and "value"

```{r example, screenshot.force=FALSE}
library(data.table)
library(witchtools)

# Creation of the initial dataset
# Note the column names: iso3 and value
gdp_iso3 <- copy(default_weights[['gdp']])
setnames(gdp_iso3,'weight','value')
gdp_iso3

```

Now, using the function `convert_region`, 
we will aggregate this dataset at country-level (ISO3) to the 17-region 
mapping of the WITCH model, available as a default mapping.

```{r convert_witch17}
# Aggregate value at WITCH regional scale (17 regions)
gdp_witch17 <- convert_region(gdp_iso3, to_reg = 'witch17')
gdp_witch17
```

In a final step, we will convert the 17-region data into the 5-region of 
the SSP database.
The dataset is first disaggregated at iso3 level then it is aggregated into 
5 regions, automatically.

```{r convert_r5}
# Aggregate value at WITCH regional scale (17 regions)
gdp_r5 <- convert_region(gdp_witch17, to_reg = 'r5')
gdp_r5
```

## Time conversion

In this section, we convert a yearly time-serie into the default time period
of the WITCH model, 5 year-periods from 2005 to 2150, using the
function `convert_time_period`.

```{r convert_t30}

# Time-serie
dd <- data.table(tech = c("tech1","tech2"), year = 2005:2050, value = 1:46)

# Aggregate values to the default WITCH time period mapping
res <- convert_time_period(dd, 't30')
print(nrow(res))
print(res, nrows = 20)

```

The function `convert_time_period` can also extrapolate the missing periods.

```{r convert_t30_extrap}

# Aggregate values to the default WITCH time period mapping with extrapolation
res <- convert_time_period(dd, 't30', do_extrap = TRUE)
print(nrow(res))
print(tail(res))
```
